### 2021-10-26 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@08cf85b4d29a6f6a51e60325d9d93a4211aecce3 🚀

We can similarly define the intersection (similarly commutative) of two
networks:

@@

One of the arguments put forth by Fründ (2021) is that the decomposition
outlined above will overestimate the effect of rewiring; I argue that
this is based on a misunderstanding of what \(\beta_{st}\) achieves. It
is paramount to clarify that \(\beta_{st}\) is not a direct measure of
the importance of turnover: it is a quantification of the relative
impact of rewiring to overall dissimilarity, which, all non-turnover
mechanisms being accounted for in the decomposition, can be explained by
turnover mechanisms. In this section, I present two numerical
experiments showing (i) that the \(\beta_{os}\) component is in fact an
accurate measure of rewiring, and (ii) that \(\beta_{st}\) captures the
consequences of species turnover, and of the interactions brought by
unique species.

@@

We can re-calculate the illustration of Fründ (2021), wherein a pair of
networks with two shared interactions (\(A = 2\)) receive either an
interaction in \(S\), in \(U\), or in both:

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\(A\) & \(S\) & \(U\) & \(\beta_{os}\) & \(\beta_{wn}\) & \(\beta_{st}\)
& \(\beta_{st}/\beta_{wn}\)\tabularnewline
\midrule
\endhead
2 & 0 & 0 & 0 & 0 & 0 &\tabularnewline
2 & 1 & 0 & \(1/5\) & \(1/5\) & 0 & 0\tabularnewline
2 & 0 & 1 & 0 & \(1/5\) & \(1/5\) & 0\tabularnewline
2 & 1 & 1 & \(1/5\) & \(1/3\) & \(2/15\) & \(2/5\)\tabularnewline
\bottomrule
\end{longtable}

The over-estimation argument hinges on the fact that
\(\beta_{st} < \beta_{os}\) in the last situation (one interaction as
rewiring, one as turnover). Reaching the conclusion of an overestimation
from this is based on a mis-interpretation of what \(\beta_{st}\) means.
The correct interpretation is that, out of the entire network
dissimilarity, only three-fifths are explained by re-wiring. The fact
that this fraction is not exactly one-half comes from the fact that the
Wilson \& Shmida (1984) measure counts shared interactions \emph{twice}
(\emph{i.e.} it has a \(2A\) term), which over-amplifies the effect of
shared interactions as the network is really small. Running the same
calculations with \(A = 10\) gives a relative importance of the turnover
processes of 47\%, and \(\beta_{st}\) goes to \(1/2\) as \(A/(S+U)\)
increases. As an additional caveat, the value of \(\beta_{st}\) will
depend on the measure of beta-diversity used. Measures that do not count
the shared interaction twice are not going to amplify the effect of
rewiring.

Based on the arguments presented above, I do not think the suggestion of
Fründ (2021) to change the denominator of \(\beta_{os}\) makes sense as
a default; the strength of the original approach by Poisot \emph{et al.}
(2012) is indeed that the effect of turnover is based on a rigorous
definition of networks as graphs (as opposed to networks as matrices),
in which the induction of vertices from the edgelist being compared
gives rise to biologically meaningful denominators. The advantage of
this approach is that at no time does the turnover of species itself (or
indeed, as shown in many places in this manuscript, the network
richness), or the connectance of the network, enter into the
calculation. As such, it is possible to use \(\beta_{os}\) and
\(\beta_{wn}\) in relationship to these terms, calculated externally (as
was recently done by \emph{e.g.} Higino \& Poisot 2021), without
creating circularities.

\textbf{TK} Therefore the argument of Fründ (2021), whereby the
\(\beta_{os}\) component should decrease with turnover, and be invariant
to connectance, does not hold: the very point of the approach is to
provide measures that can be interpreted in the light of connectance and
species turnover.

\textbf{TK} Adopting the perspective developed in the previous section,
wherein networks are sets and the measures of \(\beta\)-diversity
operates on these sets, highlights the conceptual issue in the Fründ
(2021) alternative normalization: they are using components of the
networks that are \emph{not} part of the networks being compared.

>>>>

We can similarly define the intersection (also commutative) of two
networks:

@@

One of the arguments put forth in a recent paper by Fründ (2021) is that
the decomposition outlined above will overestimate the effect of
rewiring; I argue that this is based on a misunderstanding of what
\(\beta_{st}\) achieves. It is paramount to clarify that \(\beta_{st}\)
is not a direct measure of the importance of turnover: it is a
quantification of the relative impact of rewiring to overall
dissimilarity, which, all non-turnover mechanisms being accounted for in
the decomposition, can be explained by turnover mechanisms. In this
section, I present two numerical experiments showing (i) that the
\(\beta_{os}\) component is in fact an accurate measure of rewiring, and
(ii) that \(\beta_{st}\) captures the consequences of species turnover,
and of the interactions brought by unique species.

@@

We can re-calculate the illustration of Fründ (2021), wherein a pair of
networks with two shared interactions (\(C = 2\)) receive either an
interaction in \(T\), in \(R\), or in both:

\begin{longtable}[]{@{}lllllll@{}}
\toprule
\(C\) & \(T\) & \(R\) & \(\beta_{os}\) & \(\beta_{wn}\) & \(\beta_{st}\)
& \(\beta_{st}/\beta_{wn}\)\tabularnewline
\midrule
\endhead
2 & 0 & 0 & 0 & 0 & 0 &\tabularnewline
2 & 1 & 0 & \(1/5\) & \(1/5\) & 0 & 0\tabularnewline
2 & 0 & 1 & 0 & \(1/5\) & \(1/5\) & 0\tabularnewline
2 & 1 & 1 & \(1/5\) & \(1/3\) & \(2/15\) & \(2/5\)\tabularnewline
\bottomrule
\end{longtable}

The over-estimation argument hinges on the fact that
\(\beta_{st} < \beta_{os}\) in the last situation (one interaction as
rewiring, one as turnover). Reaching the conclusion of an overestimation
from this is based on a mis-interpretation of what \(\beta_{st}\) means.
The correct interpretation is that, out of the entire network
dissimilarity, only three-fifths are explained by re-wiring. The fact
that this fraction is not exactly one-half comes from the fact that the
Wilson \& Shmida (1984) measure counts shared interactions \emph{twice}
(\emph{i.e.} it has a \(2C\) term), which over-amplifies the effect of
shared interactions as the network is really small. Running the same
calculations with \(C = 10\) gives a relative importance of the turnover
processes of 47\%, and \(\beta_{st}\) goes to \(1/2\) as \(C/(T+R)\)
increases. As an additional caveat, the value of \(\beta_{st}\) will
depend on the measure of beta-diversity used. Measures that do not count
the shared interaction twice are not going to amplify the effect of
rewiring.

Based on the arguments presented above, I do not think the suggestion of
Fründ (2021) to change the denominator of \(\beta_{os}\) makes sense as
a default; the strength of the original approach by Poisot \emph{et al.}
(2012) is indeed that the effect of turnover is based on a rigorous
definition of networks as graphs (as opposed to networks as matrices),
in which the induction of vertices from the edgelist being compared
gives rise to biologically meaningful denominators. The advantage of
this approach is that at no time does the turnover of species itself (or
indeed, as shown in many places in this manuscript, the network
richness), or the connectance of the network, enter into the calculation
of the beta-diversity components. As such, it is possible to use
\(\beta_{os}\) and \(\beta_{wn}\) in relationship to these terms,
calculated externally (as was recently done by \emph{e.g.} Higino \&
Poisot 2021), without creating circularities.

Therefore the argument of Fründ (2021), whereby the \(\beta_{os}\)
component should decrease with turnover, and be invariant to
connectance, does not hold: the very point of the approach is to provide
measures that can be interpreted in the light of connectance and species
turnover. Adopting the perspective developed in the previous section,
wherein networks are sets and the measures of \(\beta\)-diversity
operates on these sets, highlights the conceptual issue in the Fründ
(2021) alternative normalization: they are using components (namely,
interactions) of the networks that are \emph{not} directly part of the
two networks being compared.
